### 2019-05-02 reports/thesis/chapters/1_literatureReview.tex
Literature review complete

XCT started its use in the medical field but advancement of the technology saw its use in manufacturing and metrology, the science of measurement. Applications of XCT include the examination of acetabular hip prosthesis cups \citep{kourra2018computed}, skeletons \citep{appleby2014scoliosis}, batteries \citep{taiwo2017investigating} and materials \citep{zhang2016x, wang2017x}. Reverse engineering is possible when XCT is combined with AM, for example it was use for improving existing hollow engine valves \citep{cooper2015design}. However the use of XCT in metrology is not yet firmly established compared to other methods of measurement \citep{thompson2016x}. This is because is a lot of inconsistent in the setup of XCT apparatuses and on controlling the sources of error.

@@

The acquisition process consist of the production of x-rays, x-ray attenuating the object, the detection of x-rays and the reconstruction process.

@@

The electrons can interact with the anode in a number of ways. The electrons can be deflected or decelerated due to the electric field from the nucleus of the target material, the energy lost by the electrons is emitted as bremsstrahlung radiation. The energy of the bremsstrahlung radiation depends on the potential difference in the x-ray tube, as this determines the energy of the fired electrons, and also the proton number of the anode target because this affects the electric field produced by the nucleus in the anode target \citep{sun2012overview}. Another interaction is when the electrons may collide with the nucleus in the anode target, exciting an inner shell electron and ionizing it. This produce a vacancy in the electron shell and emits a photon when the excited electron drops down back to the ground state. This is known as characteristic radiation and the energy emitted is discrete and depends on the material in the anode target.

The efficiency of an x-ray tube is poor, 99\% of the electron energy is converted to heat, the rest on x-rays \citep{kruth2011computed}.

Photons are emitted from the x-ray tube as a Poisson process. The rate of x-ray emission depends on the current, that is the rate of charge between the cathode and anode. The energy of each photon are from bremsstrahlung radiation and characteristic radiation, making the distribution of x-ray photons energy a mix of continuous and discrete energies.

The object being scanned are being exposed x-ray photons in XCT. X-ray photons undergo attenuation when interacting with the object in a number of ways. The object can absorb the photons via the photoelectric effect. In the photoelectric effect, the photons transfers all its energy to a bounded electron and ejects it from the sample's atom \citep{millikan1916direct}. Photons can be scattered by the sample by colliding inelastically with and transfers its energy to the an electron. This process is known as Compton scattering \citep{compton1923quantum}. The photoelectric effect and Compton scattering make a number of photons undetectable. However if some of the photons avoid these processes, they are detected and their energy is left unaffected.

Beer's law simplifies these quantum mechanistic process. Suppose the x-ray beam with rate of emission $I_0$ is mono-energetic and travels in a straight line in the $x$-axis. Let $\mu=\mu(x)$ be the attenuation coefficient of the object and the x-ray beam has rate of emission $I$ after attenuation. A differential equation can be setup such that
\begin{equation}
\dfrac{\diff I}{\diff x} = -I\mu(x)
\end{equation}
which can be solved
\begin{equation}
I = I_0\exp\left[\int_{\text{path of photon}}-\mu(x)\diff x\right] \ .
\label{eq:beerLaw}
\end{equation}
However the photoelectric effect and Compton scattering, thus the attenuation coefficient as well, depends on the energy of the photons \citep{elbakri2002statistical}. Therefore $\mu=\mu(x,E)$ should be made dependent on the energy of the photons \citep{cantatore2011introduction}. In general low energy photons are more likely to be absorbed and scattered than high energy photons, this increases the average energy of the attenuated photons. This is called beam hardening.

After attenuation, the x-ray photons are detected by the x-ray detector. Most X-ray detectors are made up of a scintillator material \citep{curran1953luminescence, greskovich1997ceramic} and photodiodes. The x-ray photons interact with the scintiallator material and produce visible light \citep{rossner1993conversion}. The visible light is detected by photodiodes and covert it into electrical signal \citep{michael2001x}. The electrical signal can be a quantum counter, counting the number of photons detected, or an energy integrating detector, adding up all of the energies of each detected photon \citep{whiting2006properties, kruth2011computed}.

Not all of the visible light photons are detected by the photodiodes, thus not all the x-ray photons are detected. The ratio between the number of x-ray photons detected by the detector and the number of x-ray photons arriving at the detector is called the quantum efficiency \citep{cierniak2011x}.

The detection is a two stage process \citep{cierniak2011x}, although there exist equipment which detects x-ray directly such as a xenon gas ionization detector \citep{fuchs2000direct}, solid state CT systems such as sintillator-photodiodes detectors have high quantum efficiency of about 98\% to 99.5\% \citep{hsieh2000investigation}. The detectors used in CT scanning are typically flat bed scanners which consist of an array of panels of photodiodes \citep{cantatore2011introduction}. The electrical signal from the photodiodes are subject to sampling and quantisation to store these signals as an image \citep{cierniak2011x}.

%DEAD PIXELS, PANELS

Methods used to reconstruct the 3D surface of the sample are available such as filtered back-projection \citep{brooks1976principles} and the FDK algorithm \citep{feldkamp1984practical}. There exist software such as \emph{VGStudio MAX} \citep{reinhart2008industrial} which automatically aligns and scales the 3D reconstruction with the computed aided design and compares them.

Reconstruction \citep{radon1986on} There exist various reconstruction algorithms \citep{smith1990cone}

\subsection{Metrology}

@@

\subsection{X-Ray Production}
Photons in CT scanning are produced in an X-ray tube. In an X-ray tube, a cathode, consisting of a heated filament, fires projectile electrons through an electric potential to a target which forms the anode \citep{michael2001x}, as shown in Figure \ref{fig:x_ray_tube}. Most of the kinetic energy of the projectile electrons is converted into heat however some is converted into electromagnetic radiation. This depends on how the projectile electrons interact with the atoms in the anode \citep{cantatore2011introduction}.

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{figures/x_ray_tube.png}
	\caption{An X-ray tube produces photons by firing projectile electrons from a cathode to an anode. \citep{michael2001x}}
	\label{fig:x_ray_tube}
\end{figure}

Bremsstrahlung is the result of projectile electrons deaccelerating due to the electrostatic field produced by nucleus of the target. The kinetic energy of the projectile electrons is then converted to electromagnetic radiation to produce X-ray radiation. As a result, the photon energies in bremsstrahlung radiation is  a continuous spectrum and can range up to the maximum kinetic energy of the projectile electrons \citep{michael2001x}.

Characteristic radiation is due to projectile electrons colliding with electrons in the target atom and ionizing them. This produce vacancies in the electron shell and emits photons when the electrons in the target atom drops down back to the ground state. The energy of the emitted radiation is monoenergetic and depends on the binding energy of the target's atoms \citep{michael2001x}.

A typical energy spectrum of photons emitted from an X-ray tube is as shown in Figure \ref{fig:x_ray_spectrum}. The energy spectrum consist of both bremsstrahlung and characteristic radiation \citep{michael2001x}.

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{figures/x_ray_spectrum.png}
	\caption{A typical energy spectrum of photons emitted from an X-ray tube. The continuous spectrum is the result of bremmsstrahlung. The peaks are the result of characteristic radiation. \citep{michael2001x}}
	\label{fig:x_ray_spectrum}
\end{figure}

The voltage and current can be varied in the X-ray tube to produce different energy spectrums and rate of photon production. This can vary the results produced when collecting CT data \citep{cantatore2011introduction}. Another important factor is the focal spot size because smaller spot sizes produce sharper edges. Larger spot sizes produce unsharp results and this is know as the penumbra effect, as shown in Figure \ref{fig:x_ray_penumbra}. However spot sizes too small can produce concentrated heat \citep{welkenhuyzen2009industrial} and can damage the X-ray tube.

\begin{figure}
	\centering
	\includegraphics[width=1\textwidth]{figures/x_ray_penumbra.png}
	\caption{Larger focal spot sizes produces unsharp results. This is know as the penumbra effect. \emph{Source: F.~Welkenhuyzen et al.~(2009)\citep{welkenhuyzen2009industrial}}}
	\label{fig:x_ray_penumbra}
\end{figure}

\subsection{Photon Interactions}
Photons emitted by the X-ray tube are projected onto the sample and interacts with it in a number of ways \citep{cantatore2011introduction}.

The sample can effectively absorb photons via the photoelectric effect or pair production \citep{cantatore2011introduction}. In the photoelectric effect, the photons transfers all its energy to a bounded electron and ejects it from the sample's atom \citep{millikan1916direct}. In pair production, the photons convert into electron-position pairs by interacting with the Coulomb field of the sample's atomic nucleus \citep{hubbell2006electron}. In addition to getting absorbed, photons can be scattered by the sample. This happens when photons collide inelastically with and transfers its energy to the sample's electrons. This process is known as Compton scattering \citep{compton1923quantum}.

Suppose a mono-energetic X-ray pencil beam attenuating through an object with varying attenuation coefficient in position $\mu=\mu(x)$. The beam starts at $x=0$ and is detected at $x=L$, then the attenuation (decrease in X-ray intensity from $I_0$ to $I_1$) is given as \citep{cantatore2011introduction}
\begin{equation}
	I_1 = I_0\exp\left[\int_0^L-\mu(x)\diff x\right].\label{eq:beerLaw}
\end{equation}
By comparing the intensity before and after attenuation, the integral of the attenuation coefficient along the path of the X-ray can be calculated. Because of the discrete nature of pixels, the integral is usually replaced by a sum \citep{michael2001x}.

However it was shown that the attenuation coefficient does depend on the energy of the photons \citep{elbakri2002statistical}. Thus $\mu=\mu(x,E)$ should be made dependent on the energy of the photons \citep{cantatore2011introduction}. In general low energy photons are more likely to be absorbed than high energy photons, this increases the average energy of the attenuated photons and can be a source of error in CT scanning. This is referred to beam hardening and can cause inaccuracies in Equation \eqref{eq:beerLaw} \citep{michael2001x}. This can be reduced by placing a thin sheet of filter to absorb low energy photons \citep{welkenhuyzen2009industrial} or by correcting it in the data analysis stage \citep{michael2001x}.

\subsection{Detection}
Most X-ray detectors are made up of a scintillator material \citep{greskovich1997ceramic} and photodiodes. Firstly the x-ray photons interact with the scintiallator material and produce visible light \citep{rossner1993conversion}. Lastly the visible light is then detected by photodiodes and coverts it into electricical current \citep{michael2001x}. Not all of the visible light photons are detected by the photodiodes, thus not all the x-ray photons are detected. The ratio between the number of x-ray photons detected by the detector and the number of x-ray photons arriving at the detector is called the quantum efficiency \citep{cierniak2011x}.

The detection is a two stage process \citep{cierniak2011x}, although there exist equipment which detects x-ray directly such as a xenon gas ionization detector \citep{fuchs2000direct}, solid state CT systems such as sintillator-photodiodes detectors have high quantum efficiency of about 98\% to 99.5\% \citep{hsieh2000investigation}. The detectors used in CT scanning are typically flat bed scanners which consist of an array of panels of photodiodes \citep{cantatore2011introduction}. The electrical signal from the photodiodes are subject to sampling and quantisation to store these signals as an image on a computer \citep{cierniak2011x}.

\section{X-ray Computed Tomography}
Computed tomography (CT) scanning is a 3D imaging technique. It does this by reconstructing the geometry of the sample through a series of 2D X-ray images of the sample. The sample rotates after each image taken \citep{cantatore2011introduction}.

Figure \ref{fig:x_ray_ct} shows a diagram on how CT scanning works. A 2D image is taken by projecting X-ray photons onto the stationary sample. The photons are then scattered or absobred by the sample.  Some of these photons are then detected by an X-ray detector on the other side of the sample, which produces an image. After an image has been taken, the object rotates and another image is taken. Finally after a number of images, a 3D reconstruction of the object can be estimated \citep{cantatore2011introduction}.

\begin{figure}
	\centering
	\includegraphics[width=0.7\textwidth]{figures/x_ray_ct.png}
	\caption{X-ray computed tomography reconstructs the sample by projecting photons onto a rotating sample. The photons are then detected by the detector. \emph{Source: \url{http://www.phoenix-xray.com/}}}
	\label{fig:x_ray_ct}
\end{figure}

CT was solved theoretically by \cite{cormack1973reconstruction} and implemented by \cite{hounsfield1973computerized} \citep{hounsfield1980computed}. It was mainly used for medical imaging. The setup for CT scanning is different when scanning patients because the detector and X-ray source rotates around the patient \citep{cantatore2011introduction}. Recently CT has been used industrially for non-destructive testing in manufacturing \citep{cantatore2011introduction}. One possible application would be inspecting 3D printed samples \citep{villarraga2015assessing}. Other uses in science include the investigation of batteries \citep{o2017investigating} and materials \citep{wang2017x} \citep{zhang2016x}.

Methods used to reconstruct the 3D surface of the sample are available such as filtered back-projection \citep{brooks1976principles} and the FDK algorithm \citep{feldkamp1984practical}. There exist software such as \emph{VGStudio MAX} \citep{reinhart2008industrial} which automatically aligns and scales the 3D reconstruction with the computed aided design and compares them.

Studies have been done to use x-ray CT to do defection detection on 3D printing \citep{kim2016inspection} \citep{villarraga2015assessing}. This was done by investigating the variation of the material thickness and the distribution of the volume of voids \citep{villarraga2015assessing}. Voids then can be classified as defects if the voids are larger than some volume threshold. This threshold controls the probability of the detection of defects \citep{amrhein2014characterization} \citep{gandossi2010probability}.

Full 3D x-ray CT scans can be slow and may not generalised well in production lines. However there is potential to bring in methods such as those used in airport luggage inspection to speed up to process \citep{warnett2016towards}.

There are many sources of error in CT scanning \citep{cantatore2011introduction} and this can cause problems when reconstructing the geometry of the sample. Sources of error include: dead pixels in the detector \citep{brettschneider2014spatial}, use of cone beams \citep{sun2016applications}, beam hardening and the orientation of the sample \citep{corcoran2016observations}.

The scale of the 2D images can be calibrated with the use of reference standards \citep{bartscher2007enhancement} \citep{lifton2013application}.

\section{Compound Poisson}

The greyvalues of each pixel in the detector can be modelled as a random variable, due to the random behaviour of photons being produced, interacting with the phantom and interacting with the scintillator in the detector. When the photons interact with the scintillator, they are converted into visible light. The visible light photons are then detected and converted into a greyvalue. How the detected visible light is converted is important in modelling the greyvalue.

Should the greyvalue be proportional to the number of photons detected, the detector is known as a quantum counter and the greyvalue is a Poisson random variable, up to a constant \citep{whiting2006properties}. However if the greyvalue records the signal strength, proportional to the energy detected, then the detector is an energy integrating detector. The greyvalue has the compound Poisson distribution, again up to a constant \citep{whiting2006properties}. There are other types of detection schemes \citep{whiting2006properties} but it shall be not be considered here.

Experiments have been done to verify the compound Poisson nature of the detector. This was done by investigating the variance of radiographs of air \citep{hsieh2015compound} and a polyethylene cylinder \citep{yang2009evaluation} \citep{yang2010noise} at different voltages and powers. It was found there were 2 components in the noise, one was signal dependent and comes from the compound Poisson, the other was signal independent and may be electronic noise. The electronic noise can be modelled as Normally distributed \citep{xu2009electronic}.

The compound Poisson can be formally written. Let $Y$ be the number of photons detected in a pixel for some time exposure $\tau$,
\begin{equation*}
	Y\sim\poisson(\lambda)
\end{equation*}
that is
\begin{equation*}
	\prob(Y=y)=\euler^{-\lambda}\frac{\lambda^y}{y!} \quad \text{for }y=0,1,2,\dotdotdot
\end{equation*}
where $\lambda>0$ is the Poisson rate parameter. Let $U_i$ be the energy of the $i$th photon in a pixel for i.i.d.~$i=1,2,3,\dotdotdot$ with p.d.f.~$p_U(u)$. Let $X$ be the greyvalue of a pixel and is an energy integrating detector, then
\begin{equation}
	X|Y = \sum_{i=1}^{Y}U_i+\kappa
	\label{eq:compoundPoisson_X|Y}
\end{equation}
where $\kappa$ is some offset. For now let $\kappa=0$, then the marginal $X$ has the compound Poisson distribution. The p.d.f.~of $X$ can be obtained by marginalising the joint p.d.f.
\begin{equation*}
	p_X(x)=\sum_{y=0}^\infty p_{X|Y}(x|y)\prob(Y=y) \quad\text{for }x\geqslant 0
	\ .
\end{equation*}
However it should be noted that $X=0$ if and only if $Y=0$ with probability
\begin{equation*}
	\prob(X=0)=\euler^{-\lambda} \ .
\end{equation*}
Formally $X$ has probability mass at $X=0$ and probability density at $X>0$, then 
\begin{equation}
	p_X(x) = 
	\begin{cases}
		\delta(x) \euler^{-\lambda}  & \text{ for } x=0 \\ 
		\sum_{y=1}^\infty p_{X|Y}(x|y)\euler^{-\lambda}\frac{\lambda^y}{y!} \quad\text{for } & \text{ for } x>0
	\end{cases}
\end{equation}
where $\delta(x)$ is the Dirac delta function. It is quite often the case this cannot be written in closed form.

The m.g.f.~of $X$ has a nicer form however. Let the m.g.f.~of $X$ be
\begin{equation*}
	M_X(\theta)=\expectation\left[\euler^{X\theta}\right]
	\ .
\end{equation*}
This can be computed using the result for conditional expectations
\begin{equation*}
	M_X(\theta)=\expectation\expectation\left[\euler^{X\theta}|Y\right]
	\ .
\end{equation*}
Using the definition of $X|Y$ in Equation \eqref{eq:compoundPoisson_X|Y}, then
\begin{equation*}
	M_X(\theta)=\expectation\expectation\left[\exp\left(\theta U_1 + \theta U_2 + \dotdotdot + \theta U_Y\right)|Y\right]
\end{equation*}
\begin{equation*}
	M_X(\theta)=\expectation\expectation\left[\euler^{\theta U_1}\cdot\euler^{\theta U_2}\cdot\dotdotdot\cdot\euler^{\theta U_Y}|Y\right]
	\ .
\end{equation*}
But because $U_i$ for $i=1,2,3,\dotdotdot$ are i.i.d., then each $U_i$ has a common m.g.f.
\begin{equation*}
	M_U(\theta)=\expectation\left[\euler^{U\theta}\right]
	\ ,
\end{equation*}
then
\begin{equation*}
	M_X(\theta)=\expectation\left(
		\expectation\left[\euler^{\theta U_1}|Y\right]\cdot
		\expectation\left[\euler^{\theta U_2}|Y\right]\cdot
		\dotdotdot \cdot
		\expectation\left[\euler^{\theta U_Y}|Y\right]
	\right)
\end{equation*}
\begin{equation*}
	M_X(\theta)=\expectation\left[\left(M_U(\theta)\right)^Y\right]
\end{equation*}
\begin{equation*}
	M_X(\theta)=\expectation\left[\euler^{Y\ln(M_U(\theta))}\right]
\end{equation*}
\begin{equation*}
	M_X(\theta) = M_Y\left(\ln(M_U(\theta)\right)
\end{equation*}
where $M_Y(\theta)$ is the m.g.f.~of $Y$. It can be shown that the m.g.f.~of $Y$ is
\begin{equation}
	M_Y(\theta)=\expectation\left[\euler^{Y\theta}\right]=
	\exp
	\left[
		\lambda
		\left(
		  \euler^\theta-1
		\right)
	\right]
\end{equation}
then
\begin{equation}
	M_X(\theta)=
	\exp\left[
		\lambda
		\left(
			M_U(\theta)-1
		\right)
	\right]
	\ .
\end{equation}
As long as the m.g.f.~of $U$ is known, then m.g.f.~of $X$ can be written in closed form.

Moments of $X$ can be obtained from the m.g.f.~by differentiating it and setting it to zero
\begin{align*}
	M_X'(\theta)&=\exp\left[\lambda\left(M_U(\theta)-1\right)\right]\cdot\lambda M_U'(\theta) \\
	M_X'(\theta)&=M_X(\theta)\lambda M_U'(\theta)
\end{align*}
then
\begin{equation}
	\expectation\left[X\right]=\lambda\expectation\left[U\right]
	\ .
\end{equation}
Conducting the same procedure
\begin{equation*}
	M_X''(\theta)=M_X'(\theta)\lambda M_U'(\theta)+M_X(\theta)\lambda M_U''(\theta)
	\ ,
\end{equation*}
the variance can be obtained
\begin{equation*}
	\variance\left[X\right]=M_X''(0)-\left[M_X'(0)\right]^2
\end{equation*}
\begin{equation*}
	\variance\left[X\right]=M_X'(0)\lambda M_U'(0)+M_X(0)\lambda M_U''(0)-\left[\lambda\expectation\left[U\right]\right]^2
\end{equation*}
\begin{equation*}
	\variance\left[X\right]=\lambda^2 \left(\expectation\left[U\right]\right)^2+\lambda \expectation\left[U^2\right]-\left[\lambda\expectation\left[U\right]\right]^2
\end{equation*}
resulting in
\begin{equation}
	\variance\left[X\right] = \lambda\expectation\left[U^2\right]
	\ .
\end{equation}
This can be extended for higher moments.

Because the m.g.f.~can be written down in closed form, so is the characterisation function or Fourier transform of the p.d.f.~of $X$. By obtaining an empirical version of $p_U(u)$, moments of $X$ can be estimated using the m.g.f.~and the p.d.f.~can be estimated by using fast Fourier transform on the empirical characteristic function \citep{whiting2006properties}.

If the distribution of $U$ cannot be obtained or estimated, then one can guess that distribution. \cite{xu2009electronic} for example used a Gamma distribution
\begin{equation}
	U\sim\gammaDist\left(\alpha,\beta\right)
\end{equation}
where $\alpha>0$ is the Gamma shape parameter and $\beta>0$ is the Gamma rate parameter. This is a special case of the compound Poisson called the compound Poisson-Gamma model and one can write
\begin{equation}
	X\sim\CPoisson(\lambda,\alpha,\beta)
	\ .
\end{equation}
The conditional distribution can be shown to be
\begin{equation}
	X|Y\sim\gammaDist\left(Y\alpha,\beta\right)
	\ .
\end{equation}

Using results derived earlier, the m.g.f.~of the of $X$ is
\begin{equation}
	M_X(\theta)=\exp\left[\lambda\left(\left(\frac{\beta}{\beta-\theta}\right)^{\alpha}-1\right)\right]
\end{equation}
and moments can be obtained from it such as
\begin{equation}
	\expectation\left[X\right]=\frac{\alpha\lambda}{\beta}
\end{equation}
\begin{equation}
	\variance\left[X\right]=\frac{\alpha(\alpha+1)\lambda}{\beta^2}
	\label{eq:compoundPoisson_variance}
\end{equation}
and
\begin{equation}
	\expectation\left[(X-\expectation[X])^3\right] = \frac{\alpha(\alpha+1)(\alpha+2)\lambda}{\beta^3}
	\ .
\end{equation}

The p.d.f.~can be shown to be
\begin{equation}
	p_X(x) = 
	\begin{cases}
		\delta(x) \euler^{-\lambda} & \text{ for } x=0 \\ 
		\sum_{y=1}^{\infty}\frac{\beta^{y\alpha}}{\Gamma(y\alpha)}x^{y\alpha-1}\euler^{-\beta x}\euler^{-\lambda}\frac{\lambda^y}{y!} & \text{ for } x>0
	\end{cases}
	\label{eq:compoundPoisson_pdf}
\end{equation}
and it is well known the infinite sum cannot be written in closed form. There are a number of approximations or computational methods to evaluate the p.d.f.~such as Fourier inverting the characteristic function \citep{dunn2008evaluation}, using the saddlepoint approximation \citep{daniels1954saddlepoint} or cleverly sum over certain terms in the infinite sum \citep{dunn2005series}. Of course direct simulation of a compound Poisson-Gamma random variable is incredibly easy if $U$ can be simulated. The p.d.f.~then can be estimated using these simulated samples.

For a given i.i.d.~random sample of a compound Poisson-Gamma random variable, parameter estimation can be difficult. Maximum likelihood estimation is very complicated \citep{withers2011compound}. It can be made simpler by fixing $\alpha$ to be known \citep{withers2011compound} but this is not useful in this context.

>>>>

XCT started its use in the medical field but advancement of the technology saw its use in manufacturing and metrology, the science of measurement. Applications of XCT include the examination of acetabular hip prosthesis cups \citep{kourra2018computed}, skeletons \citep{appleby2014scoliosis}, batteries \citep{taiwo2017investigating} and materials \citep{zhang2016x, wang2017x}. Reverse engineering is possible when XCT is combined with AM, for example it was used for improving existing hollow engine valves \citep{cooper2015design}. However the use of XCT in metrology is not yet firmly established compared to other methods of measurement \citep{thompson2016x}. This is because there is a lot of inconsistent in the setup of XCT apparatuses and on controlling the sources of error.

@@

The acquisition process consist of the production of x-rays, x-rays attenuating the object, the detection of x-rays and the reconstruction process.

@@

The electrons can interact with the anode in a number of ways. The electrons can be deflected or decelerated due to the electric field from the nucleus of the target anode material, the energy lost by the electrons is emitted as bremsstrahlung radiation. The energy of the bremsstrahlung radiation depends on the potential difference in the x-ray tube, as this determines the energy of the fired electrons, and also the proton number of the anode target because this affects the electric field produced by the nucleus in the anode target \citep{sun2012overview}. Another interaction is when the electrons may collide with the nucleus in the anode target, exciting an inner shell electron and ionizing it. This produce a vacancy in the electron shell and emits a photon when the excited electron drops down back to the ground state. This is known as characteristic radiation and the energy emitted is discrete and depends on the material in the anode target.

The efficiency of an x-ray tube is poor, 99\% of the energy from electrons is converted to heat, the rest to x-rays \citep{kruth2011computed}.

Photons, making up the radiation, are emitted from the x-ray tube as a Poisson process. The rate of x-ray emission depends on the current, that is the rate of charge between the cathode and anode. The energy of each photon are from bremsstrahlung radiation and characteristic radiation, making the distribution of x-ray photons energy a mix of continuous and discrete energies.

The object being scanned are exposed to x-ray photons in XCT. X-ray photons undergo attenuation when interacting with the object in a number of ways. The object can absorb the photons via the photoelectric effect. In the photoelectric effect, the photons transfers all its energy to a bounded electron and ejects it from the sample's atom \citep{millikan1916direct}. Photons can be scattered by the sample by colliding inelastically with and transfers its energy to the an electron. This process is known as Compton scattering \citep{compton1923quantum}. The photoelectric effect and Compton scattering make a number of photons undetectable. However if some of the photons avoid these processes, they are detected and their energy is left unaffected.

Beer's law simplifies these quantum mechanistic process. Suppose the x-ray beam with rate of emission $I_0$ is mono-energetic and travels in a straight line in the $x$-axis. Let $\mu(x)$ be the attenuation coefficient of the object and the x-ray beam has rate of emission $I$ after attenuation. A differential equation can be set up to model the decay of photons as it attenuate through the object such that
\begin{equation}
\dfrac{\diff I}{\diff x} = -I\mu(x)
\end{equation}
which can be solved
\begin{equation}
I = I_0\exp\left[\int_{x \in \text{path of photon}}-\mu(u)\diff u\right] \ .
\label{eq:beerLaw}
\end{equation}
However, the photoelectric effect and Compton scattering, thus the attenuation coefficient as well, depends on the energy of the photons \citep{elbakri2002statistical}. Therefore $\mu(x,E)$ should be made dependent on the energy of the photons \citep{cantatore2011introduction} and can cause some inaccuracies in Beer's law. In general low energy photons are more likely to be absorbed and scattered than high energy photons, this increases the average energy of the detected photons. This is called beam hardening.

After attenuation, the x-ray photons are detected by the x-ray detector. The detectors used in XCT are typically flat bed scanners made up of a scintillator material \citep{curran1953luminescence, greskovich1997ceramic} and photodiodes. The x-ray photons interact with the scintiallator material and produce visible light \citep{rossner1993conversion}. The visible light is detected by photodiodes and coverts it into an electrical signal \citep{michael2001x}. The electrical signal can be a quantum counter, counting the number of photons detected, or an energy integrating detector, adding up all of the energies of each detected photon \citep{whiting2006properties, kruth2011computed}. The electrical signals are subject to sampling and quantisation to store these signals as an image \citep{cierniak2011x}.

Not all of the visible light photons are detected by the photodiodes, thus not all the x-ray photons are detected. The ratio between the number of x-ray photons detected by the detector and the number of x-ray photons arriving at the detector is called the quantum efficiency \citep{cierniak2011x}. The detection is a two stage process \citep{cierniak2011x}, although there exist equipment which detects x-ray directly such as a xenon gas ionization detector \citep{fuchs2000direct}, solid state CT systems such as sintillator-photodiodes detectors have high quantum efficiency of about 98\% to 99.5\% \citep{hsieh2000investigation}.

Once multiple x-ray images of the object have been acquired at multiple angles, the reconstruction process can start. The objective of reconstruction is to estimate the attenuation coefficient of the object at each point in space $\mu(x,y,z)$ using the x-ray images. It should be reminded that the x-ray images are based on the line integral of the attenuation coefficient along the path of photons. This problem was formed by \cite{radon1986on} as the `determination of functions from their integral values along certain manifolds'.

There exist many reconstruction algorithms in XCT \citep{smith1990cone} such as the filtered back-projection \citep{brooks1976principles} and the FDK algorithm \citep{feldkamp1984practical}. Once the reconstruction has been done, the shape or surface can be extracted by use of thresholding \citep{kruth2011computed}. There exist many software for the reconstruction stage of XCT \citep{reinhart2008industrial, sun2012overview}.

\subsection{Metrology in Practice}

XCT can be used to measure the length of the object, making it useful for measuring AM objects internally and externally. \emph{Nikon} offer products and services for XCT including features such as direct comparison to the CAD \citep{nikon2015microfocus, nikon2018mct225} and automated production line inspection \citep{nikon2015inline, nikon2018automated}.

As with a lot of measurement apparatus, calibration is required. In XCT, the scale of each voxel in the reconstruction can be obtained by using XCT on an object with pre-determined lengths, these are known as reference standards \citep{bartscher2007enhancement} but can have similar names. Reference standards can vary in geometry such as a sphere on a cylinder \citep{lifton2013application}, two spheres on a cylinder \citep{sun2016reference}, a cube with cut outs \citep{kiekens2011test}, a plate with various features \citep{moylan2014additive, mohring2015testpart}, a hollow cylinder, a step-cylinder and a ball-bar \citep{bartscher2007enhancement}. They can be manufactured using AM \citep{mohring2015testpart} but this can become a chicken and egg problem, determining the measurements of an AM object using an AM object.

There are many variables in XCT and a lot of them have to be controlled. For example XCT should be done in room temperature to avoid any thermal variation \citep{bryan1990international}, however this can be hard to do when the x-ray tube is a heat source \citep{kruth2011computed}.

The set up of XCT has a number of variables. The potential difference and current of the x-ray tube can be adjusted to control the contrast and brightness of the x-ray image. The exposure time is also a factor. These settings should be set high enough to avoid beam extinction but low enough that there is contrast where less material is present \citep{kruth2011computed}. The magnification can be adjusted by adjusting the distances between the x-ray tube, the object and the x-ray detector. Increasing the magnification increases the image resolution but can cause blurred images \citep{kruth2011computed}. Another important factor is the focal spot size because larger spot sizes produce blurry results, this is know as the penumbra effect \citep{kueh2016modelling}. However spot sizes too small can produce concentrated heat \citep{welkenhuyzen2009industrial} and can damage the x-ray tube. There is also the question on how to orient the object on the turntable \citep{corcoran2016observations}. All of these variables can be determined before the XCT process by use of simulations \citep{reisinger2011simulation, reiter2011simulation}, however there may be inconsistencies. For example even though the target material of the anode and power is specified, the energy spectrum can still vary \citep{stumbo2004direct}.

Problems can occur in the detector. For examples pixels in the acquired x-ray can be defected or dead \citep{brettschneider2014spatial} and panels can appear \citep{yang2009evaluation}. Spatially correlated noise can be observed as well \citep{sun2016characterisation}.

Errors due to beam hardening can occur. Low energy photons are more likely to be absorbed or scattered, this causes a few millimetres of the surface of the object to absorb or scatter more photons than the interior. This can cause flat surfaces to be barrelled and edges rounded off \citep{kruth2011computed} as well as artefacts \citep{sun2016applications}. Beam hardening can be tackled by eliminating the low energy photons by placing a thin metal plate in front of the x-ray tube \citep{welkenhuyzen2009industrial}, for example copper. This reduces the rate of photon emission but this can be compensated by increasing the exposure time \citep{kruth2011computed}. Beam hardening can also be considered in the reconstruction stage \citep{sun2016applications}.

The most common reconstruction method is the FDK \citep{feldkamp1984practical} algorithm as it caters for cone beams. However it assumes a circular trajectory from the source which can produce artefacts \citep{sun2016applications}.

@@

The most common use of XCT in AM is the investigation of pores in the manufactured object \citep{thompson2016x}. Pores can be classified as defects if the pores are larger than some volume threshold. This threshold controls the probability of the detection of defects \citep{gandossi2010probability, amrhein2014characterization}.

The porosity can be estimated by dividing the volume of all of the pores by the volume of solid material in the XCT scan \citep{taud2005porosity}. However more accurate methods of measuring the porosity can be done using Archimedes' method \citep{spierings2011comparison}. The strength of XCT comes from the fact that the location of the pores can be visualised and compared to the CAD \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}. Studies have been done to link porosity to stress concentration \citep{leuders2015fatigue, siddique2015computed, carlton2016damage}. \cite{leuders2015fatigue} pointed out that the location of the pores is an important factor. In addition to pores, any surface deviation can be measured by aligning the reconstruction with the CAD and measuring any discrepancies \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}.

One of the disadvantages of XCT is that it is a slow process. Even in the marketing of \cite{nikon2015inline}'s inline quality control featured automatic reconstruction in the background with a progress bar. The reconstruction can take between 5 minutes to a number of hours \citep{warnett2016towards}. \cite{warnett2016towards} improved the speed of XCT by sacrificing accuracy of the reconstruction. This was done by placing the object to scan on a conveyor belt surrounded by multiple x-ray source and detector pairs. X-ray images at fewer angles can be taken but they can be obtained in one acquisition, speeding up the process.

Instead of reconstructing the object, the analysis can be done on the x-ray images itself, or projection space, by comparing it to a simulation such as \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}. \cite{brierley2018optimized} developed an algorithm to adjust the parameters of the simulation as well as aligning it so that it fits with the x-ray acquisition. It is however very complicated as it is optimising over a very large dimensional space. \cite{brierley2018optimized} also demonstrated that detection of defects is possible in projection space by comparing two simulations with each other, one with defects and the other without. It is however inevitable that accuracy is lost from the jump from 3D to 2D \citep{hayden2009chest}.
